Uncertainty propagation for predictor effects and bias correction in generalized linear (mixed) models

### 2021-12-05 variable_predictions.Rnw
Figure 2 analytical soln

@@

We consider more complex interactions in which the focal predictor is modelled as a cubic polynomial. Specifically:
%
\begin{align}\label{sim:lm_cubic}
\mathrm{hh~size} &= \beta_0 + \beta_{\mathrm{A_1}}\mathrm{Age}_i + \beta_{\mathrm{A_2}}\mathrm{Age}^2_i + \beta_{\mathrm{A_3}}\mathrm{Age}^3_i + \beta_{\mathrm{W}}\mathrm{Wealthindex}_i + \epsilon_i \nonumber\\
\mathrm{Age}_i &\sim \mathrm{Normal}(0, 1) \nonumber\\
\mathrm{Wealthindex}_i &\sim \mathrm{Normal}(0, 1) \nonumber\\
\epsilon_i &\sim \mathrm{Normal}(0, 10) \nonumber\\
\beta_0 &= 20 \nonumber\\
\beta_{\mathrm{A}_1} &= 0.1 \nonumber\\
\beta_{\mathrm{A}_2} &= 0.8 \nonumber\\
\beta_{\mathrm{A}_3} &= 0.3 \nonumber\\
\beta_{\mathrm{W}} &= 0.8 \nonumber\\
i &= 1,\cdots, 100
\end{align}
%

>>>>

\newcommand{\yE}{{\mathrm E}}

@@

We consider more complex interactions in which the focal predictor is modelled as a cubic polynomial. Specifically:
%
\begin{align}\label{sim:lm_cubic}
\mathrm{hh~size} &= \beta_0 + \beta_{\mathrm{A_1}}\mathrm{Age}_i + \beta_{\mathrm{A_2}}\mathrm{Age}^2_i + \beta_{\mathrm{A_3}}\mathrm{Age}^3_i + \beta_{\mathrm{W}}\mathrm{Wealthindex}_i + \epsilon_i \nonumber\\
\mathrm{Age}_i &\sim \mathrm{Normal}(0, 1) \nonumber\\
\mathrm{Wealthindex}_i &\sim \mathrm{Normal}(0, 1) \nonumber\\
\epsilon_i &\sim \mathrm{Normal}(0, 10) \nonumber\\
\beta_0 &= 20 \nonumber\\
\beta_{\mathrm{A}_1} &= 0.1 \nonumber\\
\beta_{\mathrm{A}_2} &= 0.8 \nonumber\\
\beta_{\mathrm{A}_3} &= 0.3 \nonumber\\
\beta_{\mathrm{W}} &= 0.8 \nonumber\\
i &= 1,\cdots, 100
\end{align}
%
We may be interested in comparing the observed average household size ($\yE(\mathrm{hh~size})$) and the predicted average household size ($\yE(\widehat{\mathrm{hh~size}})$). 
%
\begin{align}\label{sim:lm_cubic_mean}
\yE(\mathrm{hh~size}) &\approx \beta_0 + \beta_{\mathrm{A_1}}\yE(\mathrm{Age}_i) + \beta_{\mathrm{A_2}}\yE(\mathrm{Age}^2_i) + \beta_{\mathrm{A_3}}\yE(\mathrm{Age}^3_i) \nonumber\\ 
	& + \beta_{\mathrm{W}}\yE(\mathrm{Wealthindex}_i)
\end{align}
%

We provide analytical comparison in two cases, i.e., when the interaction is in the focal predictor ($\mathrm{Age}$ is the focal predictor)
%
\begin{align}\label{sim:lm_cubic_analytic_age}
\eta^\star(\mathrm{Age}_i, \nset{{\overline{\mathrm{Wealthindex}}}}) &= \beta_0 + \beta_{\mathrm{A_1}}\mathrm{Age}_i + \beta_{\mathrm{A_2}}\mathrm{Age}^2_i + \beta_{\mathrm{A_3}}\mathrm{Age}^3_i \nonumber\\ 
	& + \beta_{\mathrm{W}}\overline{\mathrm{Wealthindex}} \nonumber\\
\yE({\eta^\star(\mathrm{Age}_i, \nset{{\overline{\mathrm{Wealthindex}}}})}) &= \beta_0 + \beta_{\mathrm{A_1}}\yE({\mathrm{Age}_i}) + \beta_{\mathrm{A_2}}\yE({\mathrm{Age}^2_i}) + \beta_{\mathrm{A_3}}\yE({\mathrm{Age}^3_i}) \nonumber\\ 
	& + \beta_{\mathrm{W}}\overline{\mathrm{Wealthindex}}
\end{align}
%
and when the interaction is in the non-focal predictor ($\mathrm{Wealthindex}$ is the focal predictor)
%
\begin{align}\label{sim:lm_cubic_analytic_wealthindex}
\eta^\star(\mathrm{Wealthindex}_i, \nset{{\{\overline{\mathrm{Age}}, \overline{\mathrm{Age}}^2, \overline{\mathrm{Age}}^3\}}}) &= \beta_0 + \beta_{\mathrm{A_1}}\overline{\mathrm{Age}} + \beta_{\mathrm{A_2}}\overline{\mathrm{Age}}^2 + \beta_{\mathrm{A_3}}\overline{\mathrm{Age}}^3 \nonumber\\ 
	& + \beta_{\mathrm{W}}\mathrm{Wealthindex}_i \nonumber\\
\yE(\eta^\star(\mathrm{Wealthindex}_i, \nset{{\{\overline{\mathrm{Age}}, \overline{\mathrm{Age}}^2, \overline{\mathrm{Age}}^3\}}})) &= \beta_0 + \beta_{\mathrm{A_1}}\overline{\mathrm{Age}} + \beta_{\mathrm{A_2}}\overline{\mathrm{Age}}^2 + \beta_{\mathrm{A_3}}\overline{\mathrm{Age}}^3 \nonumber\\ 
	& + \beta_{\mathrm{W}}\yE(\mathrm{Wealthindex}_i)
\end{align}
%
From Equation~\ref{sim:lm_cubic_mean} and ~\ref{sim:lm_cubic_analytic_age}
%
\begin{align*}
\yE(\mathrm{hh~size}) &\approx \yE({\eta^\star(\mathrm{Age}_i, \nset{{\overline{\mathrm{Wealthindex}}}})})
\end{align*}
%
since $\overline{\mathrm{Wealthindex}} = \yE(\mathrm{Wealthindex}_i)$. On the other hand
%
\begin{align*}
\yE(\mathrm{hh~size}) &\approx \yE(\eta^\star(\mathrm{Wealthindex}_i, \nset{{\{\overline{\mathrm{Age}}, \overline{\mathrm{Age}}^2, \overline{\mathrm{Age}}^3\}}}))
\end{align*}
%
if and only if $\yE(\mathrm{Age^2}) = \yE(\mathrm{Age}) \yE(\mathrm{Age})$ and $\yE(\mathrm{Age^3}) = \yE(\mathrm{Age}) \yE(\mathrm{Age}) \yE(\mathrm{Age})$, but, without loss of generality, for example 
%
\begin{align}
\yE(\mathrm{Age^2}) &= \yE(\mathrm{Age}) \yE(\mathrm{Age}) + \sigma^2_{\mathrm{Age}} \nonumber\\
&= \overline{\mathrm{Age}}^2 + \sigma^2_{\mathrm{Age}}
\end{align}
%
